External priors for the next generation of CMB experiments.

### 2016-02-24 Notes/CMBS4_priors_paper.tex
very minor changes

\reffig{prior_neff} shows projections for how well CMB-S4 will do at measuring $N_{\rm eff}$ as a function of priors on $H_{0}$, $\Omega_{c}h^{2}$ and $\Omega_{b}h^{2}$ (the sum of the neutrino masses must be included as a free parameter). With no priors on the other parameters, the projected $1$-sigma error is $0.016$, close to a 3-sigma detection of the expected deviation from $N_{\rm eff}=3$.

@@

Much of the improvement that would come on neutrino masses and $w$ from $H_0$ or $\Omega_ch^2$ priors is anticipated to be provided by distance measurements made by DESI. But, additional $H_0$ measurements beyond DESI would help, as evidenced by the sharply falling curves in the left-most regions of \reffig{prior_omeganuh2-h}, \reffig{prior-50}, \reffig{prior_neff} and \reffig{prior_w-h}. Indeed, perhaps the most tantalizing finding is that future surveys beyond DESI and LSST \cite{lsst-dark-energy-science-collaboration:2012} that would tighten the constraints on, say, $n_s$ could indirectly lead to constraints in $N_{\rm eff}$ much less than a percent. Given the power of these constraints to probe physics beyond the Standard Model, such surveys seem particularly interesting to pursue.

>>>>

\reffig{prior_neff} shows projections for how well CMB-S4 will do at measuring $N_{\rm eff}$ as a function of priors on $H_{0}$, $\Omega_{b}h^{2}$ and $\Omega_{c}h^{2}$ (the sum of the neutrino masses must be included as a free parameter). With no priors on the other parameters, the projected $1$-sigma error is $0.016$, close to a 3-sigma detection of the expected deviation from $N_{\rm eff}=3$.

@@

Much of the improvement that would come on neutrino masses and $w$ from $H_0$ or $\Omega_ch^2$ priors is anticipated to be provided by distance measurements made by DESI. But, additional $H_0$ measurements beyond DESI would help, as evidenced by the sharply falling curves in the left-most regions of \reffig{prior_omeganuh2-h}, \reffig{prior-50}, and \reffig{prior_w-h}. Furthermore, perhaps the most tantalizing finding is that future surveys beyond DESI and LSST \cite{lsst-dark-energy-science-collaboration:2012} that would tighten the constraints on, say, $n_s$ could indirectly lead to constraints in $N_{\rm eff}$ much less than a percent. Given the power of these constraints to probe physics beyond the Standard Model, such surveys seem particularly interesting to pursue.
